---
title: "data analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      collapse = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      comment = "#>"
                      )
```

---

## EXPLORATION

### 1. Study sites

```{r, fig.height=7, eval=FALSE}
readd(Q10_map)$gg_facet
```

```{r map_studies, fig.height=4, fig.width=8}
readd(Q10_map)$gg_species
```


### 2. Studies by Climate

#### 2.1. Climate regions
```{r map_biomes, fig.height=5, fig.width=8}
readd(gg_mat_map)$map_climate_regions_all
```

#### 2.2. MAT-MAP spread of data
```{r studies_biomes, fig.height=4.5, fig.width=5}
readd(gg_mat_map)$gg_data_mat_map
```


### 3. How many datapoints?

Datapoints: 

```{r}
readd(study_summary)$datapoints_co2 %>% knitr::kable()
```

total datapoints:
```{r}
readd(study_summary)$total_datapoints %>% knitr::kable()
```
  
Studies: 

```{r}
readd(study_summary)$study_counts %>% knitr::kable()
```

total studies:
```{r}
readd(study_summary)$total_studies %>% knitr::kable()
```


### 4. Incubation Temperature Ranges

#### 4.1. summary of incubation temperatures
```{r temp_ranges_seg, fig.height=7, fig.width=7.5}
readd(gg_temp_ranges)
```

#### 4.2. Q10 vs. incubation temperatures
```{r temp_ranges_q10, fig.height=5, fig.width=12}
readd(gg_temp_ranges_q10)
```

#### 4.3. incubation temperature ranges
```{r temp_ranges_box, fig.height=4, fig.width=12}
readd(gg_temp_ranges_field_lab)
```


---

---

## Analysis

### 1. Summary tables

#### 1.1. Overall summary

```{r}
readd(summary_tables)$summary_overall %>% 
  mutate(across(where(is.numeric), round, 2)) %>% 
  knitr::kable()
```

#### 1.2. By biome

```{r}
readd(summary_tables)$summary_biome %>% 
  mutate(across(where(is.numeric), round, 2)) %>% 
  knitr::kable()

```

#### 1.3. By incubation temperature

```{r}
readd(summary_tables)$summary_temp %>% 
  mutate(across(where(is.numeric), round, 2)) %>% 
  knitr::kable()

```


### 2. CO2: All studies, all temperatures

We included all datapoints collected, irrespective of incubation temperature range. (0-10 C, 0-15 C, 0-20 C, 10-20 C, 5-15 C, etc.)

**ANOVA**
```{r}
readd(co2_all)$aov_all
```


```{r co2_all_data, fig.height=4, fig.width=9}
library(patchwork)

a = readd(co2_all)$gg_raincloud_all
b = readd(co2_all)$gg_temp_scatter

a + b +
  plot_annotation(tag_levels = "A")

```


### 3. CO2: Temp ranges of 10 C only

We then subset the data to include only incubations with temperature ranges of 10 C.  
(0-10 C, 10-20 C, 5-15 C, 15-25 C, etc.)

```{r co2_10C, fig.height=4, fig.width=4}
readd(co2_all)$gg_raincloud_tenC
readd(co2_all)$aov_tenC

```


### 4. Grouping by biome

```{r co2_biome, fig.height=4, fig.width=8}
readd(co2_biome)$gg_biome_raincloud
```

#### 5. Grouping by Ecosystem type

```{r, fig.height=4, fig.width=8}
readd(co2_ecosystem)$gg_ecosystem_raincloud

readd(co2_ecosystem)$co2_ecosystem_summary %>% knitr::kable()


```


#### 5. Grouping by Measurement type
```{r, fig.height=4, fig.width=8}
readd(co2_measurement)$gg_measurement_raincloud

readd(co2_measurement)$co2_measurement_summary %>% knitr::kable()

```



### 5. Subsetting by temperature range

We then subset the data to include only incubations with specific temperature ranges: < 5 C, 5-15 C, 15-25 C, > 25C. These ranges were chosen because these ranges had the highest frequency of data, and this would also avoid issues pertaining to frozen soils (if we were tp choose 0-10 C).


```{r co2_temp_range, fig.height=4, fig.width=7}
readd(co2_temp_range)$resp_q10_temp_raincloud
```

**ANOVA**
```{r, fig.height=4, fig.width=7}
readd(co2_temp_range)$co2_aov_temp
```



#### 5.1. Bootstrapping the data

The data were highly skewed toward the field measurements, because most came from the highly curated SRDB. To do a more balanced analysis, we did bootstrapping by randomly sampling 1000 times, 10 samples each. 

```{r co2_bootstrapping, fig.height=3.5, fig.width=7}
readd(co2_bootstrapping)$gg_boot_raincloud
readd(co2_bootstrapping)$gg_boot_density
```

**ANOVA on bootstrapped data**
```{r}
readd(co2_bootstrapping)$boot_aov
```


#### 5.2 Combining non-bootstrap and bootstrap plots

```{r co2_temp_bootst, fig.height=7, fig.width=7}
library(patchwork)

non_boot = readd(co2_temp_range)$resp_q10_temp_raincloud
boot = readd(co2_bootstrapping)$gg_boot_raincloud

non_boot / boot +
  plot_annotation(tag_levels = "A")

```




### 6. Heterotrophic respiration

The field measurements reported above included both autotrophic and heterotrophic respiration, whereas the lab measurements refer only to heterotrophic. We subset field measurements that were heterotrophic respiration only, and compared that with lab.

The heterotrophic field measurements were available for temperate and snow biomes only.

```{r co2_rh, fig.height=5, fig.width=6}
readd(Q10_rh_only)$means
readd(Q10_rh_only)$gg_q10_rh

```

- How did field Rh vs. lab Rh compare?
```{r}
readd(Q10_rh_only)$aov_rh_lab
```

- How did field Rh vs. field Ra compare?
```{r}
readd(Q10_rh_only)$aov_rh_ra_field
```


---

### 7. Analysis - CH4

```{r ch4_all, fig.height=4, fig.width=4}
readd(ch4_all)$gg_ch4_raincloud
```

**ANOVA**
```{r}
readd(ch4_all)$ch4_aov
```



---

<details>   
   <summary>Session Info</summary>
   
Date run: `r Sys.Date()`

```{r}
sessionInfo()
```

</details> 